\documentclass[a4paper,10pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.25in}
\addtolength{\evensidemargin}{-0.25in}
\addtolength{\textwidth}{0.5in}
\addtolength{\topmargin}{-.25in}
\addtolength{\textheight}{0.5in}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\vspace{-6pt}]

% Bullet points formatting
\setlist[itemize]{noitemsep, topsep=0pt}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\centerline{\huge \bf Anurag Kumar}
\centerline{\href{mailto:your.email@example.com}{your.email@example.com} \quad|\quad +91-XXXXXXXXXX \quad|\quad \href{https://github.com/Anurag-xo}{GitHub: Anurag-xo} \quad|\quad \href{https://your-portfolio-link.com}{Portfolio}}

\section{Summary}
DevOps Engineer with hands-on experience in Linux server administration, cloud-native deployments, CI/CD automation, containerization, and infrastructure monitoring. Skilled in Docker, Kubernetes, Helm, Argo CD, and AWS. Adept at collaborating with cross-functional teams, optimizing deployment pipelines, and delivering scalable, secure, and high-availability systems.

\section{Skills}
\textbf{DevOps \& Cloud:} Docker, Kubernetes, Helm, Argo CD, AWS, Terraform, Prometheus, Grafana \\
\textbf{Programming \& Scripting:} Bash, Python, Node.js, C++, YAML \\
\textbf{Linux \& Networking:} Linux Administration, System Hardening, Networking Protocols, Firewall Configuration \\
\textbf{CI/CD Tools:} GitHub Actions, Jenkins, Git, GitOps \\
\textbf{Databases:} MongoDB, MySQL

\section{Experience}
\textbf{DevOps Intern} \hfill Bhilai Steel Plant \quad (May 2024 – Jul 2024) \\
\begin{itemize}
    \item Collaborated with stakeholders to gather requirements, design, and implement Linux-based server solutions ensuring high availability and optimal performance.
    \item Configured and maintained web servers, performed security hardening, and implemented firewall rules.
    \item Troubleshot and resolved application issues, documenting solutions for future reference.
    \item Provided guidance on best practices for system usage to internal teams.
\end{itemize}

\section{Projects}
\textbf{ShellCraft – Advanced Shell Scripting Automation Toolkit} \hfill \href{https://github.com/Anurag-xo/shellcraft}{GitHub Link} \\
\begin{itemize}
    \item Developed a suite of shell scripts for Linux automation covering system setup, network configuration, and package management.
    \item Implemented modular scripting with error handling and logging for reliability.
\end{itemize}

\textbf{EmailNotification Microservice – Event-Driven Notification System} \hfill \href{https://github.com/Anurag-xo/EmailNotification-microservice}{GitHub Link} \\
\begin{itemize}
    \item Built a Node.js-based microservice for sending automated email notifications triggered by events.
    \item Deployed using Docker containers with CI/CD pipeline integration.
\end{itemize}

\textbf{Cloud-Native CI/CD Pipeline with Kubernetes \& GitOps} \\
\begin{itemize}
    \item Designed and deployed a complete CI/CD pipeline using GitHub Actions, Argo CD, and Kubernetes for zero-downtime deployments.
    \item Integrated automated testing, security scans, and monitoring with Prometheus \& Grafana.
    \item Implemented infrastructure-as-code using Terraform for AWS provisioning.
\end{itemize}

\section{Education}
\textbf{B.Tech in Computer Science and Engineering (AIML)} \hfill Shri Shankaracharya Technical Campus (2021 – 2025) \\
Expected Result: \textbf{8.5/10 CGPA} \\
\textbf{Higher Secondary (Class 12)} – CBSE: \textbf{88\%} \\
\textbf{Secondary (Class 10)} – CBSE: \textbf{90\%}

\section{Achievements \& Certifications}
\begin{itemize}
    \item Google Cybersecurity Certificate
    \item Completed cloud-native projects with Kubernetes, Helm, and Argo CD
    \item Active open-source contributor on GitHub
\end{itemize}

\end{document}

